\section{Materials}
Every material used in the project have been uploaded. It is possible to find:
\begin{itemize}
    \item the datasets on the \href{https://drive.google.com/drive/folders/1XHGu-9OgFi-b95f1fKpOvqIJvS_YHhO1?usp=sharing}{Google Drive folder};
    \item the code on the \href{https://github.com/fedeizzo/camera-pose-estimation}{GitHub repository}.
\end{itemize}

The project has been developed in Python 3, using common data science libraries, such as numpy, pandas, PyTorch, matplotlib, scipy, aim and many others.

\subsection{Repository organization}
The repository follows the structure:
\begin{itemize}
    \item \texttt{camera-pose-estimation/}
    \begin{itemize}
        \item \texttt{model/} contains everything related to the deep learning part of the project. It also includes the code used for implementing the web-server under \texttt{webserver.py} and \texttt{static/}.
        \item \texttt{tools/} contains scripts used for the dataset generation pipeline.
    \end{itemize}
    \item \texttt{config\_parser/}: Python package written by us that allows to create configuration files, with the idea of improving reproducibility in our experiments. Each configuration file can be subdivided in sections: for each section you can define variables with the sintax \texttt{label=value}, where \texttt{value} is a parsable JSON object (boolean, int, float, list, object).
    \item \texttt{docs/} contains the project report and presentation.
    \item \texttt{notebooks/} contains some Python Jupyter Notebooks that have been used for data exploration, validation, and post-processing of the model predictions.
\end{itemize}

\subsection{Data organization}
For each footage, a folder has been created:
\begin{itemize}
    \item \texttt{imgs/} contains the video frames exported with ffmpeg;
    \item \texttt{processed\_dataset/} contains the train, validation, and test datasets that can be reused during different trainings: this helps speeding up the loading procedure;
    \item \texttt{workspace/} contains the models generated by COLMAP;
    \item each of \texttt{train.csv}, \texttt{validation.csv}, and \texttt{test.csv} contains a table for specifying the pose for each frame. These files can be generated with the \texttt{video\_to\_dataset.sh} script.
\end{itemize}

For more information please refer to the GitHub repository.
